Condition-Based Maintenance for Complex Systems\\ based on Current Component Status\\ and Bayesian Updating of Component Reliability

### 2016-10-21 cbm-rbd-paper.tex
change posterior parameters notation

@@

\section{***summary of ASCE-ASME paper method minus sets of priors}

@@

test data inclusion
(write down explicit formula for test data including censored observations),
noninformatiove censoring

RUL via survival signature,
posterior predictive distributions,
system reliability curve (RUL) as output,

@@

***RUL model description below follows closely \cite{2016:walter-coolen},
which describes the same RUL model.
However, \cite{2016:walter-coolen} does not consider maintenance policies,
and focuses on a generalization of the RUL model using sets of priors for the component models
(effectively parametric P-boxes),
allowing for vague and partial prior specifications,
and sensitivity to prior-data conflict.

@@

Using \eqref{eq:abtony} and \eqref{eq:ig-update}, the posterior distribution over $\lambda_k$ is
\begin{align}
\lambda_k \mid \nkz, \ykz, \vec{t}_k \sim \ig(\nkz + e_k + 1, \nkz \ykz + \tautk)\,.
\label{eq:ig-update-alpha}
\end{align}
%where we have added the prior parameters $\nkz$ and $\ykz$ in notation
%to emphasize that the posterior is a synthesis of prior information and data.
As this posterior \eqref{eq:ig-update-alpha} can be defined in terms of
the updated, posterior parameters $\nkn$ and $\ykn$,
we may also write
\begin{align*}
f(\lambda_k \mid \nkz, \ykz, \vec{t}_k) &= f(\lambda_k \mid \nkn, \ykn)\,.
\end{align*}
The iterative nature of Bayesian inference means that we can take the updated,
posterior parameters as new prior parameters and update them again using new data.
Indeed, we will use this property to use the extra information about components
that accumulates during operation of the system:
At any time $\tnow > 0$,
all non-failed components correspond to a right censored observation $\tpnow$;
any failed components instead contribute a fully observed, non-censored lifetime,
and both types of observations can be used in the update step \eqref{eq:ig-update}.
To keep notation simple,
we will below denote the parameters of the inverse Gamma distribution by $\nkz$ and $\ykz$,
regardless of them expressing expert information alone,
or stemming from the combination of expert information and test data.

\section{Reliability functions for complex systems using the survival signature}
\label{sec:sysrel}

The goal is to find, for a given monitored system, the system reliability curve $\Rsys(t)$ at current time $\tnow$,
and we will now show how the system reliability function, given component models, can be efficiently calculated using the survival signature.
This system reliability gives us the RUL distribution on which we base our adaptive maintenance policy.

We consider systems of arbitrary reliability block diagram layout,
consisting of components of $K$ different types,
where there are $n_k$ components of type $k$ in the system,
and the total number of components in the system is $\sum_{k=1}^K n_k = n$.
This system is observed until time $\tnow$,
leading to censored observation of certain component lifetimes within the system.

@@

\section{Component posterior predictive distributions***}
\label{sec:postpred}

To calculate the current system reliability curve,
we thus need the probabilities $P(C^k_t = l_k)$,
which give the number of components that function at times $t > \tnow$.
In our Bayesian framework, these probabilities are given
by a so-called predictive distribution that can be derived from the distribution over $\lambda$.
This distribution needs to account for expert knowledge and test data;
following our comment at the end of Section~\ref{sec:weibull},
we assume here that ***change notation to $n_k^{(\text{test})}$ and $n_k^{(\text{now})}$???

but also for the information gained from the current run of the system:
both failure times of components (if any)
and the right-censoring time $\tnow$ for each non-failed component in the system
can be used to update $\nkz$ and $\ykz$.

In analogue to the notation from Section~\ref{sec:weibull},
let $n_k = e_k^{\tnow} + c_k^{\tnow}$ be the number of type $k$ components in the monitored system,
where $e_k^{\tnow}$ is the number of components that have failed by $\tnow$,
and $c_k^{\tnow}$ is the number of components that have not failed by $\tnow$.
We can thus collect these observations, as of $\tnow$, in a vector
$\vec{t}_k^{\tnow} = (t_{k,1}, \ldots, t_{k,e_k}, \tpnow, \ldots, \tpnow)$,
containing $n_c$ right-censored obsevations $\tpnow$.

Furthermore, the fact that the components in the system that still function have reached the age $\tnow$
must be used when calculating the posterior predictive distribution.

\section{***from reliability curve (RUL) to maintenance decision}

>>>>

\def\yknow{y_k^{(\tnow)}}
\def\nknow{n_k^{(\tnow)}}

@@

\section{***Adaptive system RUL / RLD based on Weibull component models}

@@

test data inclusion
with noninformatiove right-censoring

RUL/RLD via survival signature,
posterior predictive distributions,
system reliability distribution (RUL/RLD) as output,

@@

***RUL model description below follows closely \cite{2016:walter-coolen},
which describes the same RUL/RLD model.
However, \cite{2016:walter-coolen} does not consider maintenance policies,
and focuses instead on a generalization of the RUL/RLD model using sets of priors for the component models
(which can be seen as parametric P-boxes),
allowing for vague and partial prior specifications,
and sensitivity to prior-data conflict \cite[\S 2.2.3.3]{diss}.

@@

Using \eqref{eq:abtony} and \eqref{eq:ig-update}, the posterior distribution over $\lambda_k$ is
\begin{align}
\lambda_k \mid \nkz, \ykz, \vec{t}_k \sim \ig(\nkz + e_k + 1, \nkz \ykz + \tautk)\,.
\label{eq:ig-update-alpha}
\end{align}
%where we have added the prior parameters $\nkz$ and $\ykz$ in notation
%to emphasize that the posterior is a synthesis of prior information and data.
As this posterior \eqref{eq:ig-update-alpha} can be defined in terms of
the updated, posterior parameters $\nkn$ and $\ykn$,
we may also write
\begin{align*}
f(\lambda_k \mid \nkz, \ykz, \vec{t}_k) &= f(\lambda_k \mid \nkn, \ykn)\,.
\end{align*}
The iterative nature of Bayesian inference means that we can take the updated,
posterior parameters as new prior parameters and update them again using new data.
Indeed, we will use this property to use the extra information about components
that accumulates during operation of the system:
At any time $\tnow > 0$,
all non-failed components correspond to a right censored observation $\tpnow$;
any failed components instead contribute a fully observed, non-censored lifetime,
and both types of observations can be used in the update step \eqref{eq:ig-update}.
Before we write this out formally in Section~\ref{sec:postpred},
we will first present how system reliability functions can be derived based on component models.
%To keep notation simple,
%we will below denote the parameters of the inverse Gamma distribution by $\nkz$ and $\ykz$,
%regardless of them expressing expert information alone,
%or stemming from the combination of expert information and test data.

\subsection{Reliability functions for complex systems using the survival signature}
\label{sec:sysrel}

Here we describe how system reliability functions, given fixed component models,
can be efficiently calculated using the survival signature.
We will show in Section~***
how this method can be used to find the system reliability function $\Rsys(t)$ at current time $\tnow$ for a monitored system,
giving us the RUL/RLD distribution on which we base our adaptive maintenance policy.

We consider systems of arbitrary reliability block diagram layout,
consisting of components of $K$ different types,
where there are $n_k$ components of type $k$ in the system,
and the total number of components in the system is $\sum_{k=1}^K n_k = n$.
An example is given in Figure~***.
Note that this system cannot be described as a nesting of series and parallel subsystems.
%This system is observed until time $\tnow$,
%leading to censored observation of certain component lifetimes within the system.

@@

\subsection{Component posterior predictive distributions}
\label{sec:postpred}

To calculate the current system reliability curve,
we thus need the probabilities $P(C^k_t = l_k)$,
which give the number of components that function at times $t > \tnow$.
In the Bayesian framework, these probabilities are given
by a so-called posterior predictive distribution that can be derived from the posterior over $\lambda$.

Denote by $\nkn$ and $\ykn$ the parameters obtained
by updating the prior parameters $\nkz$ and $\ykz$ using test data.
The corresponding distribution $f(\lambda_l \mid \nkn, \ykn)$
thus accounts for both expert knowledge and test data.
However, following our comments at the end of Section~\ref{sec:weibull},
the component models can be further updated
using information gained from the current run of the system until $\tnow$:
Any failure times of failed components,
and the right-censoring time $\tpnow$ for each non-failed component
can be used to update $\nkn$ and $\ykn$.
We denote the resulting parameter values by $\nknow$ and $\yknow$.
(It is of course possible to update $\nkz$ and $\ykz$ directly to $\nknow$ and $\yknow$ if no test data is available.)
%Furthermore, the fact that the components in the system that still function have reached the age $\tnow$
%must be used when calculating the posterior predictive distribution.

In analogue to the notation from Section~\ref{sec:weibull},
let $n_k = e_k^{\tnow} + c_k^{\tnow}$ be the number of type $k$ components in the monitored system,
where $e_k^{\tnow}$ is the number of components that have failed by $\tnow$,
and $c_k^{\tnow}$ is the number of components that have not failed by $\tnow$.
We can thus collect these observations, as of $\tnow$, in a vector
$\vec{t}_k^{\tnow} = (t_{k,1}, \ldots, t_{k,e_k}, \tpnow, \ldots, \tpnow)$,
containing $c_k^{\tnow}$ right-censored observations $\tpnow$.

\section{Dynamic maintenance policy based on the current system reliability function (RUL/RLD)}
